KidsAIR wood stove grades and usage

### 2020-12-04 stove_grade_usage_cleaning.Rmd
analysis updates

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(zoo)
```

@@

kids_kw_report_clean <- kids_kw_report %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id")) %>%  
  arrange(area, home_winter_id) %>% 
  mutate(filter_type = fct_collapse(filter_type,
                                    "Honeywell" = "Honeywell",
                                    "Large Filtrete" = "Large Filtrete",
                                    "Small Filtrete" = "Small Filtrete",
                                    "Winix" = c("Winix", "winix"))) %>% 
  mutate(kw_perc_expected = if_else(kw_hours == -999, 999999, kw_perc_expected),
         kw_perc_expected = abs(kw_perc_expected)) %>% 
  replace_with_na(replace = list(kw_perc_expected = 999999)) %>% 
  mutate(kw_perc_expected = as.numeric(kw_perc_expected))

@@

kw_perc_exp_summary <- kids_kw_report_clean %>% 
  filter(!is.na(kw_perc_expected)) %>% 
  #filter(area == "WMT") %>% 
  group_by(filter_type) %>% 
  summarize("Mean KW % Exp" = mean(kw_perc_expected),
            "SD KW % Exp" = sd(kw_perc_expected),
            "N KW % Exp" = n(),
            "Min KW % Exp" = min(kw_perc_expected),
            "25Q KW % Exp" = quantile(kw_perc_expected, 0.25),
            "Med KW % Exp" = median(kw_perc_expected),
            "75Q KW % Exp" = quantile(kw_perc_expected, 0.75),
            "Max KW % Exp" = max(kw_perc_expected))
kw_perc_exp_summary

@@

>>>>

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(zoo)
library(gridExtra)
```

@@

kids_kw_report_clean <- kids_kw_report %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id")) %>%  
  arrange(area, home_winter_id) %>% 
  mutate(filter_type = fct_collapse(filter_type,
                                    "Honeywell" = "Honeywell",
                                    "Large Filtrete" = "Large Filtrete",
                                    "Small Filtrete" = "Small Filtrete",
                                    "Winix" = c("Winix", "winix"))) %>% 
  mutate(kw_perc_expected = if_else(kw_hours == -999, 999999, kw_perc_expected),
         kw_perc_expected = if_else(kw_hours == 1000, 999999, kw_perc_expected),
         kw_perc_expected = abs(kw_perc_expected)) %>% 
  replace_with_na(replace = list(kw_perc_expected = 999999)) %>% 
  mutate(kw_perc_expected = as.numeric(kw_perc_expected)) 
  filter(treatment_assigned == "Filter")

@@

kw_perc_exp_summary <- kids_kw_report_clean %>% 
  filter(!is.na(kw_perc_expected)) %>% 
  #filter(area == "WMT") %>% 
  group_by(treatment_assigned) %>% 
  summarize("Mean KW % Exp" = mean(kw_perc_expected),
            "SD KW % Exp" = sd(kw_perc_expected),
            "N KW % Exp" = n(),
            "Min KW % Exp" = min(kw_perc_expected),
            "25Q KW % Exp" = quantile(kw_perc_expected, 0.25),
            "Med KW % Exp" = median(kw_perc_expected),
            "75Q KW % Exp" = quantile(kw_perc_expected, 0.75),
            "Max KW % Exp" = max(kw_perc_expected))
kw_perc_exp_summary

png("Kids_KW_perc_exp.png", width=960, height=480, bg = "white")
grid.table(kw_perc_exp_summary)
dev.off()

@@

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
pm_data <- 
  read_rds(paste0(file_path, "Output/health_exposure_data_sampling_day.rds")) %>% 
  arrange(area, home, pm_mean_sampling_period) %>% 
  distinct(area, home, .keep_all = TRUE) %>% 
  select(area, home, pm_mean_sampling_period)
kids_kw_report_clean <- 
  read_rds(paste0(file_path, "Output/kids_kw_report_clean.rds"))

kw_perc_exp_summary <- kids_kw_report_clean %>% 
  left_join(pm_data, by = c("area", "home")) %>% 
  filter(!is.na(kw_perc_expected)) %>% 
  #filter(area == "WMT") %>% 
  group_by(filter_type, treatment_assigned) %>% 
  summarize("Mean KW % Exp" = mean(kw_perc_expected),
            "SD KW % Exp" = sd(kw_perc_expected),
            "N KW % Exp" = n(),
            "Min KW % Exp" = min(kw_perc_expected),
            "Med KW % Exp" = median(kw_perc_expected),
            "Max KW % Exp" = max(kw_perc_expected),
            "Mean PM" = mean(pm_mean_sampling_period, na.rm = TRUE),
            "Min PM" = min(pm_mean_sampling_period, na.rm = TRUE),
            "Med PM" = median(pm_mean_sampling_period, na.rm = TRUE),
            "Max PM" = max(pm_mean_sampling_period, na.rm = TRUE))
kw_perc_exp_summary

png("Kids_KW_perc_exp.png", width=1200, height=480, bg = "white")
grid.table(kw_perc_exp_summary)
dev.off()
```

# Try to extract sampling dates from KW hour data
```{r}
wmt_sampling_dates <- read_csv(paste0(file_path, "Input/WMT/homewinter.csv"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, interventiondate, 
         samplingdate, pickupdate) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         intervention_date = ymd(interventiondate),
         sampling_date = ymd(samplingdate),
         pickup_date = ymd(pickupdate),
         area = "WMT") %>% 
  select(home_winter_id, intervention_date, 
         sampling_date, pickup_date, area)

nn_sampling_dates <- read_csv(paste0(file_path, "Input/NN/homewinter.csv"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, interventiondate, 
         samplingdate, pickupdate) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         intervention_date = mdy(interventiondate),
         sampling_date = mdy(samplingdate),
         pickup_date = mdy(pickupdate),
         area = "NN") %>% 
  select(home_winter_id, intervention_date, 
         sampling_date, pickup_date, area)

ak_sampling_dates <- read_csv(paste0(file_path, "Input/AK/homewinter.csv"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, interventiondate, 
         samplingdate, pickupdate) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         intervention_date = mdy(interventiondate),
         sampling_date = mdy(samplingdate),
         pickup_date = mdy(pickupdate),
         area = "AK") %>% 
  select(home_winter_id, intervention_date, 
         sampling_date, pickup_date, area)

kids_sampling_dates <- rbind(wmt_sampling_dates, nn_sampling_dates, ak_sampling_dates)

file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
kids_kw_clean <- 
  read_rds(paste0(file_path, "Output/kids_kw_clean.rds"))
filter_units <- 
  read_rds(paste0(file_path, "Output/kids_kw_report_clean.rds")) %>% 
  select(home_winter_id, area, filter_type)

kids_kw_dates <- kids_kw_clean %>% 
  full_join(kids_sampling_dates, by = c("area", "home_winter_id")) %>% 
  mutate(filter_var = if_else(kw_date == sampling_date | kw_date == pickup_date, 1, 0)) %>% 
  filter(filter_var == 1) %>% 
  arrange(area, home, kw_date) %>% 
  mutate(kw_diff = lead(kw_hours) - kw_hours) %>% 
  filter(!is.na(kw_diff)) %>% 
  mutate(date_diff = as.duration(interval(sampling_date, pickup_date)),
         date_diff = as.numeric(date_diff)/86400) %>% 
  left_join(filter_units, by = c("area", "home_winter_id")) %>% 
  mutate(multiplier = if_else(filter_type == "Honeywell" & treatment_assigned == "Placebo",
                              2.04, 0),
         multiplier = if_else(filter_type == "Honeywell" & treatment_assigned == "Filter",
                              4.224, multiplier),
         multiplier = if_else(filter_type == "Small Filtrete" & treatment_assigned == "Placebo",
                              0.888, multiplier),
         multiplier = if_else(filter_type == "Small Filtrete" & treatment_assigned == "Filter",
                              1.896, multiplier),
         multiplier = if_else(filter_type == "Large Filtrete" & treatment_assigned == "Placebo",
                              1.896, multiplier),
         multiplier = if_else(filter_type == "Large Filtrete" & treatment_assigned == "Filter",
                              3.48, multiplier),
         multiplier = if_else(filter_type == "Winix" & treatment_assigned == "Placebo",
                              0.0144, multiplier),
         multiplier = if_else(filter_type == "Winix" & treatment_assigned == "Filter",
                              0.48, multiplier)) %>% 
  mutate(kw_expected = date_diff*multiplier,
         kw_perc_exp = kw_diff/kw_expected*100)

file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
pm_data <- 
  read_rds(paste0(file_path, "Output/health_exposure_data_sampling_day.rds")) %>% 
  arrange(area, home, pm_mean_sampling_period) %>% 
  distinct(area, home, .keep_all = TRUE) %>% 
  select(area, home, pm_mean_sampling_period)

kw_perc_exp_summary <- kids_kw_dates %>% 
  left_join(pm_data, by = c("area", "home")) %>% 
  filter(!is.na(kw_perc_exp)) %>% 
  #filter(area == "WMT") %>% 
  group_by(filter_type, treatment_assigned) %>% 
  summarize("Mean KW % Exp" = mean(kw_perc_exp),
            "SD KW % Exp" = sd(kw_perc_exp),
            "N KW % Exp" = n(),
            "Min KW % Exp" = min(kw_perc_exp),
            "Med KW % Exp" = median(kw_perc_exp),
            "Max KW % Exp" = max(kw_perc_exp),
            "Mean PM" = mean(pm_mean_sampling_period, na.rm = TRUE),
            "Min PM" = min(pm_mean_sampling_period, na.rm = TRUE),
            "Med PM" = median(pm_mean_sampling_period, na.rm = TRUE),
            "Max PM" = max(pm_mean_sampling_period, na.rm = TRUE))
kw_perc_exp_summary

png("Kids_KW_perc_exp_sampling.png", width=1200, height=480, bg = "white")
grid.table(kw_perc_exp_summary)
dev.off()
```

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

kids_kw_clean <- 
  read_rds(paste0(file_path, "Output/kids_kw_clean.rds"))

filter_units <- 
  read_rds(paste0(file_path, "Output/kids_kw_report_clean.rds")) %>% 
  select(home_winter_id, area, filter_type)

wmt_sampling_dates <- read_csv(paste0(file_path, "Input/WMT/homewinter.csv"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, interventiondate, 
         samplingdate, pickupdate) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         intervention_date = ymd(interventiondate),
         sampling_date = ymd(samplingdate),
         pickup_date = ymd(pickupdate),
         area = "WMT") %>% 
  select(home_winter_id, intervention_date, 
         sampling_date, pickup_date, area)

nn_sampling_dates <- read_csv(paste0(file_path, "Input/NN/homewinter.csv"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, interventiondate, 
         samplingdate, pickupdate) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         intervention_date = mdy(interventiondate),
         sampling_date = mdy(samplingdate),
         pickup_date = mdy(pickupdate),
         area = "NN") %>% 
  select(home_winter_id, intervention_date, 
         sampling_date, pickup_date, area)

ak_sampling_dates <- read_csv(paste0(file_path, "Input/AK/homewinter.csv"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, interventiondate, 
         samplingdate, pickupdate) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         intervention_date = mdy(interventiondate),
         sampling_date = mdy(samplingdate),
         pickup_date = mdy(pickupdate),
         area = "AK") %>% 
  select(home_winter_id, intervention_date, 
         sampling_date, pickup_date, area)

kids_sampling_dates <- rbind(wmt_sampling_dates, nn_sampling_dates, ak_sampling_dates)

kids_kw_filtered <- kids_kw_clean %>% 
  group_by(area, home_winter_id) %>% 
  mutate(lag_diff = kw_hours - lag(kw_hours)) %>% 
  filter(lag_diff >= 0 | is.na(lag_diff)) %>% 
  mutate(lag_diff = kw_hours - lag(kw_hours)) %>% 
  filter(lag_diff >= 0 | is.na(lag_diff)) %>% 
  mutate(lag_diff = kw_hours - lag(kw_hours)) %>% 
  filter(lag_diff >= 0 | is.na(lag_diff)) %>% 
  mutate(lag_diff = kw_hours - lag(kw_hours)) %>% 
  mutate(max_kw_hours = if_else(kw_hours == max(kw_hours), 1, 0)) %>% 
  filter(max_kw_hours == 1) %>% 
  left_join(kids_sampling_dates, by = c("area", "home_winter_id")) %>% 
  mutate(date_diff = as.duration(interval(intervention_date, kw_date)),
         date_diff = as.numeric(date_diff)/86400) %>% 
  left_join(filter_units, by = c("area", "home_winter_id")) %>% 
  mutate(multiplier = if_else(filter_type == "Honeywell" & treatment_assigned == "Placebo",
                              2.04, 0),
         multiplier = if_else(filter_type == "Honeywell" & treatment_assigned == "Filter",
                              4.224, multiplier),
         multiplier = if_else(filter_type == "Small Filtrete" & treatment_assigned == "Placebo",
                              0.888, multiplier),
         multiplier = if_else(filter_type == "Small Filtrete" & treatment_assigned == "Filter",
                              1.896, multiplier),
         multiplier = if_else(filter_type == "Large Filtrete" & treatment_assigned == "Placebo",
                              1.896, multiplier),
         multiplier = if_else(filter_type == "Large Filtrete" & treatment_assigned == "Filter",
                              3.48, multiplier),
         multiplier = if_else(filter_type == "Winix" & treatment_assigned == "Placebo",
                              0.0144, multiplier),
         multiplier = if_else(filter_type == "Winix" & treatment_assigned == "Filter",
                              0.48, multiplier)) %>% 
  mutate(kw_expected = date_diff*multiplier,
         kw_perc_exp = kw_hours/kw_expected*100)

pm_data <- 
  read_rds(paste0(file_path, "Output/health_exposure_data_sampling_day.rds")) %>% 
  arrange(area, home, pm_mean_sampling_period) %>% 
  distinct(area, home, .keep_all = TRUE) %>% 
  select(area, home, pm_mean_sampling_period)

kw_perc_exp_summary <- kids_kw_filtered %>% 
  left_join(pm_data, by = c("area", "home")) %>% 
  filter(!is.na(kw_perc_exp)) %>% 
  #filter(area == "WMT") %>% 
  group_by(filter_type, treatment_assigned) %>% 
  summarize("Mean KW % Exp" = mean(kw_perc_exp),
            "SD KW % Exp" = sd(kw_perc_exp),
            "N KW % Exp" = n(),
            "Min KW % Exp" = min(kw_perc_exp),
            "Med KW % Exp" = median(kw_perc_exp),
            "Max KW % Exp" = max(kw_perc_exp),
            "Mean PM" = mean(pm_mean_sampling_period, na.rm = TRUE),
            "Min PM" = min(pm_mean_sampling_period, na.rm = TRUE),
            "Med PM" = median(pm_mean_sampling_period, na.rm = TRUE),
            "Max PM" = max(pm_mean_sampling_period, na.rm = TRUE))
kw_perc_exp_summary

png("Kids_KW_perc_exp_new.png", width=1200, height=480, bg = "white")
grid.table(kw_perc_exp_summary)
dev.off()  
```
